---
title: "Accessing SpaMTP Experiment Data"
author: "Tianyao Lu"
date: "2026-08-14"
output:
  BiocStyle::html_document:
    toc: true
vignette: >
  %\VignetteIndexEntry{Accessing SpaMTP Experiment Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

`SpaMTPData` makes the experiment data used in SpaMTP workflows discoverable
through ExperimentHub. The package itself remains small and users download only
the resources required for a particular workflow.

```{r}
library(SpaMTPData)
resources <- SpaMTPDataResources()
resources[c("resource", "version", "category")]
```

# Loading a dataset

After ExperimentHub ingestion, the mouse brain/DHB object is retrieved and
cached with:

```{r eval=FALSE}
striatum <- SpaMTPData("mouse_brain_dhb_striatum")
```

The same interface can use a previously downloaded local file:

```{r eval=FALSE}
options(SpaMTPData.resource_dir = "/path/to/SpaMTPData-files")
striatum <- SpaMTPData("mouse_brain_dhb_striatum", offline = TRUE)
```

# Session information

```{r}
sessionInfo()
```
